Transient Variability In Vapor Intrusion And The Factors That Influence It

### 2019-03-01 tex/main.tex
Updated figures

\begin{figure}[!h]
	\centering
	\begin{minipage}[c]{0.49\textwidth}
		\centering
    \caption{ }
    \label{fig:asu_phase}
    \includegraphics[width=\textwidth]{asu_phase.pdf}
	\end{minipage}
	%\hspace{3cm}
	\begin{minipage}[c]{0.49\textwidth}
		\centering
    \caption{ }
    \label{fig:indianapolis_species}
    \includegraphics[width=\textwidth]{indianapolis_species.pdf}
	\end{minipage}
\end{figure}

\subsection{Seasonal Variability}

\begin{figure}[htb!]
  \caption{ }
  \label{fig:seasonal_analysis}
  % ASU/North Island plot
  \begin{subfigure}{0.49\textwidth}
    \centering
    \caption{ }
    \label{fig:seasonal_analysis_asu}
    \includegraphics[width=\textwidth]{asu_closed_season.pdf}
  \end{subfigure}
  % Indianapolis plot
  \begin{subfigure}{0.49\textwidth}
    \centering
    \caption{ }
    \label{fig:seasonal_analysis_indianapolis}
    \includegraphics[width=\textwidth]{indianapolis_pce_season.pdf}
  \end{subfigure}
\end{figure}

\subsection{Maximum Change in Indoor Air Contaminant Concentration}

@@

\begin{figure}[htb!]
  \caption{ }
  \label{fig:simulation_sampling}
  % ASU/North Island plot
  \begin{subfigure}{0.49\textwidth}
    \centering
    \caption{ }
    \label{fig:simulation_sampling_pp_open}
    \includegraphics[width=\textwidth]{sampling_simulation_pp_open.pdf}
  \end{subfigure}
  % Indianapolis plot
  \begin{subfigure}{0.49\textwidth}
    \centering
    \caption{ }
    \label{fig:simulation_sampling_pp_closed}
    \includegraphics[width=\textwidth]{sampling_simulation_pp_closed.pdf}
  \end{subfigure}
\end{figure}

>>>>

\begin{figure}[!h]
		\centering
    \caption{ }
    \label{fig:pair_grid}
    \includegraphics[width=\textwidth]{simple_grid.pdf}
\end{figure}

@@

\begin{figure}[htb!]
  \caption{ }
  \label{fig:simulation_sampling}
  % ASU/North Island plot
  \begin{subfigure}{0.49\textwidth}
    \centering
    \caption{ }
    \label{fig:simulation_sampling_pp_open}
    \includegraphics[width=\textwidth]{simulation_prediction_span_open.pdf}
  \end{subfigure}
  % Indianapolis plot
  \begin{subfigure}{0.49\textwidth}
    \centering
    \caption{ }
    \label{fig:simulation_sampling_pp_closed}
    \includegraphics[width=\textwidth]{simulation_prediction_span_closed.pdf}
  \end{subfigure}
\end{figure}
